MS797 Glossary

### 2022-02-05 _academics/ms797-glossary/ms797-glossary.Rmd
correct term

studentized residual (98)
: a residual divided by its estimated standard error; observations with student errors higher than 3 (indicating 3 standard deviations) are likely outliers

>>>>

studentized residual (98)
: a residual divided by its estimated standard error; observations with student residuals higher than 3 (indicating 3 standard deviations) are likely outliers
